\begin{itemize}
\item \textbf{ATLAS talks (approval talks, ATLAS weekly, or open presentations):}
  \begin{itemize}
    \item 2016, ATLAS Muon Week, "MDT CSM Demonstrator for Phase II"
    \item 2015, US ATLAS Workshop, "Simulation on Triggerless Operation of the Muon MDT TDC"
    \item 2014, CERN REU, "Chamber Service Module Readback for the ATLAS Muon System"
  \end{itemize}

\item \textbf{Hardware, software, performance and other service work contributions:}
  \begin{itemize}
  \item We developed an interface to read the configuration and correct single event upsets of an FPGA located on the ATLAS muon front end Chamber Service Module (CSM) board. This work addressed a performance issue for the CSM during LHC Run 1.
  \item We simulated the latency of the muon front end electronics. The simulation addresses the increase in data volume faced by ATLAS during Phase II operation. We also built a test bench with Phase I electronics to validate the simulation.
  \item We developed a prototype Chamber Service Module designed to meet the increased data rate for ATLAS during Phase II operation. The CSM was implemented on a Kintex development board. We separately developed a device designed to send fake TDC data to the CSM for input and a DAQ system in order to validate the CSM's performance.
  \item We tested the prototype CSM at a CERN beam test. The CSM was integrated into a readout chain involving other prototype electronics that have been developed for Phase II. The CSM performed as expected.
  \item We developed a FPGA based JTAG master designed to be installed on a GBT based CSM for Phase II. The goal of this system is to supplement the missing JTAG functionality of the GBT and allow the GBT based CSM to communicate with old Mezzanine cards.
  \end{itemize}

\item \textbf{Analysis Contributions:}
  \begin{itemize}
    \item For the $H\to\mu\mu$ search, I worked on studying the contribution of VH production to the sensitivity of the dimuon channel.
  \end{itemize}
\end{itemize}

