\subsection{Publications since Sept. 2017}
\begin{itemize}
  \item Search for heavy Majorana or Dirac neutrinos and right-handed $W$ gauge bosons in final states with two charged leptons and two jets
        at $\sqrt{s} = 13$ TeV with the ATLAS detector~\cite{Aaboud:2018spl}.
        \\
        Major contribution: contact editor, analysis framework for opposite-sign channel, event selection optimization, background estimation, systematic uncertainty.
  \item A search for the rare decay of the Standard Model Higgs boson to dimuons in pp collisions at $\sqrt{s}$ = 13 TeV with the ATLAS detector~\cite{ATLAS-CONF-2018-026}.
        \\
        Major contribution: analysis framework and event selections for the VH and ttH channel.
  \item Prospect study of electroweak production of a Z boson pair plus two jets at the HL-LHC~\cite{ATL-PHYS-PUB-2018-029}.
        \\
        Major contribution: contact editor, analysis framework and event selections.
\end{itemize}


\subsection{Corresponding analysis supporting note}
\begin{itemize}
  \item Search for heavy Majorana or Dirac neutrinos and right-handed $W$ gauge bosons in final states with two charged leptons and two jets at
        $\sqrt{s}$ = 13 TeV with the ATLAS detector.
        \\
        (https://cds.cern.ch/record/2267874)
  \item Search for the dimuon decay of the Higgs boson in pp collisions at $\sqrt{s}$ = 13 TeV with the ATLAS detector.
        \\
        (https://cds.cern.ch/record/2311225)
  \item Study of electroweak production of ZZ plus two jets with high luminosity LHC.
        \\
        (https://cds.cern.ch/record/2639856)
\end{itemize}


\subsection{International Conference Talks}
\begin{itemize}
  \item Vector boson scattering, triple gauge-boson final states and limits on anomalous quartic gauge couplings with the ATLAS detector.
        CLHCP2017. 22-24 December 2017. Nanjing, China.
        \\
        (https://indico.ihep.ac.cn/event/7102/session/9/contribution/66)
  \item Measurements of VBS (and other diboson processes at high energy).
        HL/HE-LHC2108. 4-6 April 2018. Fermilab, USA.
        \\
        (https://indico.fnal.gov/event/16151/session/3/contribution/71)
  \item Results for Neutral Diboson Channels (including aTGCs): ZZ,Zy.
        MBI2018. 28-30 August 2018. Ann Arbor, USA.
        \\
        (https://indico.cern.ch/event/700961/contributions/3069893)
\end{itemize}


\subsection{On going physics analyses}
\begin{itemize}
  \item Evidence of electronweak production of ZZ plus two jets in the four leptons and two leptons plus two neutrinos channel. Publication next year.
  \item Search for rare decay of the Standard Model Higgs boson to dimuons. Publication next year.
  \item Search for Z' in the low mass region using four-lepton events under Z mass region. Publication next year.
  \item Search for HH production in the bbZZ channel. Longer term studies. Publication plan unclear.
  \item Low mass four muons study. Consistency check between 8 and 13 TeV data. Publication plan unclear.
\end{itemize}


\subsection{Service work}
\begin{itemize}
  \item MDT operation and Maintenance.
  \item Muon control room shift.
\end{itemize}


\subsection{Leadership roles}
\begin{itemize}
  \item 2018-10-01 to
        \\
        Convener of Subgroup Quarkonia production and B cross-section measurements.
  \item Nov. 2018 to
        \\
        SM group derivation production manager.
  \item Contact editor of the electroweak ZZjj analysis.
  \item Contact editor of the heavy neutrino analysis.
  \item Contact editor of the ZZ prospects study at the HL-LHC.
\end{itemize}



















