\begin{itemize}

\item \textbf{Papers and conference notes:}

    \begin{itemize}
       
      \item "Measurement of the $ZZ$ Production Cross Section in $pp$ Collisions at $\sqrt{s}=13$ TeV 
            with the ATLAS Detector", PRL 116, 101801 (2016)~\cite{atlas_run2_SM_ZZ4l_2016}

      \item "$ZZ$ cross-section measurements and aTGC search in $13$ TeV collisions with the ATLAS detector",
            ATLAS-CONF-2017-031~\cite{atlas_run2_SM_ZZ4l_2017}

      \item "$ZZ$ cross-section measurements and aTGC search in $13$ TeV collisions with the ATLAS detector",
            "To have the public reading, to submit to PRD"

            1> Total uncertainty is 5\% level, compared to RUN1 8.5\%; 2> aTGC limits are around $2\times10^{-3}$,
            compared to RUN1 $5\times10^{-3}$, decreasing by a factor of $2.5$.

      \item Search for an invisibly decaying Higgs boson or dark matter candidates produced in association with a 
            Z boson in pp collisions at $\sqrt{s}$~=~13 TeV with the ATLAS detector, "signed off by PubCom and to submit to 
            PLB" 

            1> Expected limit decreases from 60\% at 95\% CL of RUN1 to 40\% of RUN2.

      \item ``llvv SM/Higgs : share with Wen Guo''

      \item ``4l Higgs : share with Nan Lu''

    \end{itemize}

\item \textbf{Analysis Contributions:}

    \begin{itemize}
      \item For SM ZZ 4l measurement at 13TeV in 2016: the Contact of this analysis; Derived the analysis strategy and 
       fake background estimations; Compare SM ZZ4l with H4l; Help production team to fix the bug of missing event
       in data productions.

      \item For SM ZZ 4l differential measurment in 2017: Event selection studies; Trigger efficiency and scale factor studies;
      4-electron events validations.

      \item Search of Higgs invisible decays at 13TeV in HZZ group: Event selections optimization; MC sample validations; 
       Responsible for official Ntuples (MiniTree) production; Theory uncertainty studies (PDF, QCD scale and showering)
       for signal and di-boson processes. Background studies (for processes of WZ and non-resonant components) including the 
       related systematics. Contact editor. 

      \item High mass Higgs search at 13TeV in HZZ group with ZZ 2l2v: Event selections optimization; MC sample validations;
       responsible for official Ntuples (MiniTree) production; Theory uncertainty studies (PDF, QCD scale and showering)
       for signal and di-boson processes. Background studies (for processes of WZ and non-resonant components) including the
       related systematics. Derive the efficiency and yield of ggZZ in VBF category. 

      \item Higgs 4l analysis (coupling, mass, differential cross section): Baseline event selections studies and optimization;
       PDF and QCD scale uncertainties on qqZZ. 

    \end{itemize}

\item \textbf{Conference talks :}

    \begin{itemize}
        \item 11/2014, IEEE-NSS-2014, Poster of "Online precision gas evaluation of the ATLAS muon 
              spectrometer during LHC Run I"
        \item 08/2015, 2015 Meeting of the APS Division of Particles and Field, 
            ``Physics prospects of the ZZ production measurements with the ATLAS experiment at LHC RUN2'', 
            https://indico.cern.ch/event/361123
        \item 08/2016, QCD@LHC 2016, "BSM decays of the SM Higgs (rare decays, NMSSM, H->invisible etc.) and 
            non-resonant di-Higgs results", https://indico.cern.ch/event/516210
    \end{itemize}

\item \textbf{ATLAS talks (approval talks, ATLAS weekly, or open presentations):}

    \begin{itemize}
        \item 07/2016, ATLAS Approval talk, ``Analysis of Z($\to\ell\ell$)+$E_{T}^{miss}$ in HZZ group'',\\
              https://indico.cern.ch/event/558782
        \item 06/2017, Report on ATLAS Weekly, "Search for an Invisibly Decaying Higgs Boson and Dark Matter 
              Candidates Produced in Association with a $Z$ Boson in $pp$ Collisions at $\sqrt{s}=13$ TeV 
              with the ATLAS Detector", https://indico.cern.ch/event/626968 
    \end{itemize}

\item \textbf{Leadership roles (convenership, contact person, contact editor):}

    \begin{itemize}
        \item 2015-2016, Contact person for cross section measurement of di-boson ZZ with four-lepton channel. 
        \item 2016-2017, Contact editor for search for Higgs invisibly decay and Dark Matter associated with a Z boson in HZZ group.
        \item 2016-2017, Contact person for differential measurement of di-boson ZZ with two-lepton and two-neutrino channel.
    \end{itemize}

\item \textbf{Hardware, software, performance and other service work contributions:}
        \begin{itemize}
            \item On-call and maintenance of MDT Gas Monitor system (from 2014 to present)
            \item Maintenace of analysis framework "QuickAna" for RUN-II analysis. 
        \end{itemize}



\end{itemize}
